On the Functionality of the Multilayer Perceptron Classifier Neural Network Architecture

### 2020-05-31 Thesis/MLP Notes/MLP.tex
26 May 2020
- Updates to MLP breakdown
31 May 2020
- Progress on MLP paper

\begin{equation}
\label{cost func}
J : \big\{ \vec{x}^{L-1} , \hat{\theta} \big\} \rightarrow \big\{ \mathbb{R} \big\}
\end{equation}

\paragraph*{}The larger the value outputted from this function $J$, the further the models prediction differed from the expected value. Thus, this function can be through of as a measurement of how \textit{poor} the network's predict was. It then becomes appropriate to make the goal of the model to \textit{optimize} $J$, with respect the parameters $\hat{\theta}$ to allow for a generally low cost value for a given input.

>>>>

\begin{equation}
\label{cost func}
J : \big\{ \vec{x}^{(L-1)}} \rightarrow \big\{ \mathbb{R} \big\}
\end{equation}

\paragraph*{}The larger the value outputted from this function $J$, the further the models prediction differed from the expected value. Thus, this function can be through of as a measurement of how \textit{poor} the network's prediction was. It then becomes appropriate to make the goal of the model to \textit{optimize} $J$, with respect the parameters $\hat{\theta}$ to allow for a generally low cost value for a given input.

\paragraph*{}There are many ways to optimize the parameters in a neural network,for this work, we will examine an optimizer algorithm called \textit{Stochastic Gradient Descent} (SGD). This is an iterative method that uses repeated a passes over a data set to slowly push the cost function to a smaller and smaller value. As the name implies, we compute the gradient of the cost function, which its the partial derivative of each element that makes up the function, at a given step.

\paragraph*{}To compute the gradient of the cost function, we have to examine it's composition.
